A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add reference to client/server geometry developments
Add visualisation workshop reference to Appendix A

The working group will also work towards a more convenient access to geometry and
event data, through a client-server interface. In collaboration with the
Data Access and Management Working Group, an API or a service to deliver streamed
event data would be designed.

@@

The workshop that was held as part of the CWP process was felt to be
extremely useful for exchanging knowledge between developers in
different experiments, fostering collaboration and in bringing in ideas
from outside the community. This will now be held as an annual event and
will facilitate work on the common R\&D plan.

>>>>

The working group will also work towards a more convenient access to geometry and
event data, through a client-server interface~\cite{1742-6596-898-7-072015}. In collaboration with the
Data Access and Management Working Group, an API or a service to deliver streamed
event data would be designed.

@@

The workshop that was held as part of the CWP process
(\emph{HSF Visualization Workshop}, see Appendix \ref{appendix-a---list-of-workshops})
was felt to be
extremely useful for exchanging knowledge between developers in
different experiments, fostering collaboration and in bringing in ideas
from outside the community. This will now be held as an annual event and
will facilitate work on the common R\&D plan.
